### 2013-07-24 doc/asplos14/evaluation.tex
scaling

\TODO{FINISH}
Our current

>>>>

\begin{figure}[ht]
    \begin{center}
      \includegraphics[height=0.5\textwidth]{results/plot_scaling.pdf}
    \end{center}
    \caption{Scaling for BFS, IntSort, and Pagerank. Refer to Figure~\cite{fig:grappa-gups} for GUPS scaling and Figure~\cite{fig:grappa-uts} for UTS scaling}
    \label{fig:grappa-scaling}
\end{figure}

Figures~\cite{fig:grappa-scaling}, \cite{fig:grappa-gups}, and
\cite{fig:grappa-uts} show scaling out to 64 nodes. Grappa scales best
on BFS and worst on IntSort, but is in general able to make use of
more nodes. Unfortunately memory limitations in our current network
library keep us from exploring scaling beyond 64 nodes; this will be
addressed in future work.

In the limit, aggregation does not scale: the time it takes to
aggregate enough random requests to build a buffer of reasonable size
scales with the size of the cluster. However, we believe our current
approach will work for clusters with hundreds of nodes. In the future,
we will explore hierarchical, collective techniques to aggregate
requests from multiple nodes as well; we believe this can apply to
clusters with thousands of nodes.
